Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization.

### 2022-05-31 manuscript.Rmd
change font

---
title: "Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization."
output:
  bookdown::pdf_document2:
    latex_engine: "xelatex"
    toc: false
linestretch: 1
bibliography: references.bib
abstract: "`r paste0(readLines('abstract.md'), collapse = ' ')`"
---

@@

options(
  tikzDefaultEngine = "xetex",
  tikzXelatexPackages = c(getOption("tikzXelatexPackages"), "\\usepackage{amsfonts}")
)
```

@@

```{r, dev = "tikz", warning=FALSE}
vary_alpha_long %>%
  ggplot() +
  geom_line(aes(alpha, h2, linetype = certainty)) +
  lims(x = c(0, 1), y = 0:1) +
  geom_ribbon(data = vary_alpha, aes(x = alpha, ymin = uncertain, ymax = certain), alpha = .1) +
  labs(caption = "$p(E|H) = .8$, $p(H) = .1$",
       y = "$\\mathbb{E}\\big(p(H|E)\\big)$",
       x = "$\\alpha$") +
  theme_tufte() +
  theme(legend.position = c(.85, .8),
        legend.title = element_blank())
```

>>>>

---
title: "Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization."
output:
  bookdown::pdf_document2:
    latex_engine: "xelatex"
    toc: false
header-includes:
   - \usepackage{libertine}
fontsize: 11pt
linestretch: 1.2
geometry: "left=3.9cm, right=3.3cm, top=2.5cm, bottom=3cm"
papersize: a4
bibliography: references.bib
abstract: "`r paste0(readLines('abstract.md'), collapse = ' ')`"
---

@@

options(
  tikzDefaultEngine = "xetex",
  tikzXelatexPackages = c(getOption("tikzXelatexPackages"), "\\usepackage{amsfonts}", "\\usepackage{libertine}")
)
```

@@

```{r, dev='tikz'}
#| fig.cap: "Corroboration as firmness ($p(E|H)$) as a function of α, where α is either certain (solid line) or maximally uncertain (dotted line)."
vary_alpha_long %>%
  ggplot() +
  geom_line(aes(alpha, h2, linetype = certainty)) +
  lims(x = c(0, 1), y = 0:1) +
  geom_ribbon(data = vary_alpha, aes(x = alpha, ymin = uncertain, ymax = certain), alpha = .1) +
  labs(caption = "$p(E|H) = .8$, $p(H) = .1$",
       y = "$\\mathbb{E}\\big(p(H|E)\\big)$",
       x = "$\\alpha$") +
  theme_tufte() +
  theme(legend.position = c(.85, .8),
        legend.title = element_blank())
```
